01_LH-SIP_Data_Reduction

### 2022-03-29 01_LH-SIP_Data_Reduction.Rmd
moved assimilation efficiency chunk up

@@

```{r}
# Reduce the 0d --> 3d --> 7d incubation data
peaks_mapped_with_zeros_analytes_reduced <- peaks_mapped_with_zeros_analytes %>% 
  mutate(time_course = "0d -->") %>%
  # Column reduction
  select(file_id,
         sample_id,
         terrain,
         soil,
         inc_time_d,
         inc_time_d_str,
         compound,
         rel_area_FID,
         area_FID,
         d2H_mn_zero,
         d2H,
         at2H_mn_zero,
         F_0_at2H_se,
         at2H,
         area2_mn_zero,
         area2,
         area_FID,
         compound_ug_per_g_soil,
         `2F_Me`,
         `2F_FAME`,
         `2F_alk`,
         F_label_mn,
         F_label_se,
         time_course
  ) %>% 
  # Turn all unit dbls into unitless
  mutate(
    across(
      where(is.numeric),
      as.numeric
    )
  )

peaks_mapped_with_threes_analytes_reduced <- peaks_mapped_with_threes_analytes %>% 
  # Filter out 0d data points from this dataset
  filter(inc_time_d != 0) %>% 
  # Add a time course tag
  mutate(time_course = "3d -->") %>% 
  # Column reduction
  select(file_id,
         sample_id,
         terrain,
         soil,
         inc_time_d,
         inc_time_d_str,
         compound,
         rel_area_FID,
         area_FID,
         d2H_mn_three,
         d2H,
         at2H_mn_three,
         F_0_at2H_se,
         at2H,
         area2_mn_three,
         area2,
         area_FID,
         compound_ug_per_g_soil,
         `2F_Me`,
         `2F_FAME`,
         `2F_alk`,
         F_label_mn,
         F_label_se,
         time_course
  ) %>% 
  # Convert all unit dbls into unitless
  mutate(
    across(
      where(is.numeric),
      as.numeric
    )
  )
```

```{r}
d2H_assim_lm <- d2H_assim %>% 
  # Select columns of interest
  select(
    org_id,
    exp_id,
    Analyte,
    `Water dD`,
    `Lipid dD`
  ) %>% 
  drop_na() %>% 
  # Group by organism, experiment, analyte
  group_by(
    org_id,
    exp_id,
    Analyte
  ) %>% 
  # Filter out samples with three or fewer observations
  # (so that we can do a linear model)
  filter(n() > 3) %>% 
  tidyr::nest(
    data = c(`Water dD`, `Lipid dD`)
  ) %>% 
  mutate(
    fit = purrr::map(data, ~lm(`Lipid dD` ~ `Water dD`, data = .x)),
    estimates = purrr::map(fit, broom::tidy),
    summary = purrr::map(fit, broom::glance)
  ) %>% tidyr::unnest(estimates)

# Simplify by only looking at the slopes
d2H_assim_lm_summary <- d2H_assim_lm %>% 
  filter(term == "`Water dD`")
```

>>>>

```{r}
# Find Fatty acid analytes manually

fas_in_d2H_assim <- d2H_assim %>% 
  filter(str_detect(Analyte, "acid") |
           str_detect(Analyte, "ate")) %>% 
  pull(Analyte) %>% 
  unique()

d2H_assim_lm <- d2H_assim %>% 
  # Select columns of interest
  select(
    org_id,
    exp_id,
    Analyte,
    `Water dD`,
    `Lipid dD`
  ) %>% 
  # Filter to only look at FAs
  filter(Analyte %in% fas_in_d2H_assim) %>% 
  drop_na() %>% 
  # Group by organism, experiment, analyte
  group_by(
    org_id,
    exp_id,
    Analyte
  ) %>% 
  # Filter out samples with three or fewer observations
  # (so that we can do a linear model)
  filter(n() > 3) %>% 
  tidyr::nest(
    data = c(`Water dD`, `Lipid dD`)
  ) %>% 
  mutate(
    fit = purrr::map(data, ~lm(`Lipid dD` ~ `Water dD`, data = .x)),
    estimates = purrr::map(fit, broom::tidy),
    summary = purrr::map(fit, broom::glance)
  ) %>% tidyr::unnest(estimates)

# Simplify by only looking at the slopes
# This is what gets added to the peaks_mapped dataframes!
d2H_assim_lm_summary <- d2H_assim_lm %>% 
  ungroup() %>% 
  filter(term == "`Water dD`") %>% 
  summarize(sa = sd(estimate, na.rm = TRUE),
            a_mn = mean(estimate, na.rm = TRUE))
```

@@

```{r}
# Reduce the 0d --> 3d --> 7d incubation data
peaks_mapped_with_zeros_analytes_reduced <- peaks_mapped_with_zeros_analytes %>% 
  mutate(time_course = "0d -->") %>%
  # Column reduction
  select(file_id,
         sample_id,
         terrain,
         soil,
         inc_time_d,
         inc_time_d_str,
         compound,
         rel_area_FID,
         area_FID,
         d2H_mn_zero,
         d2H,
         at2H_mn_zero,
         F_0_at2H_se,
         at2H,
         area2_mn_zero,
         area2,
         area_FID,
         compound_ug_per_g_soil,
         `2F_Me`,
         `2F_FAME`,
         `2F_alk`,
         F_label_mn,
         F_label_se,
         time_course
  ) %>% 
  # Turn all unit dbls into unitless
  mutate(
    across(
      where(is.numeric),
      as.numeric
    )
  ) %>% 
  # Add assimilation efficiency data
  mutate(
    a = d2H_assim_lm_summary$a_mn,
    sa = d2H_assim_lm_summary$sa
  )

peaks_mapped_with_threes_analytes_reduced <- peaks_mapped_with_threes_analytes %>% 
  # Filter out 0d data points from this dataset
  filter(inc_time_d != 0) %>% 
  # Add a time course tag
  mutate(time_course = "3d -->") %>% 
  # Column reduction
  select(file_id,
         sample_id,
         terrain,
         soil,
         inc_time_d,
         inc_time_d_str,
         compound,
         rel_area_FID,
         area_FID,
         d2H_mn_three,
         d2H,
         at2H_mn_three,
         F_0_at2H_se,
         at2H,
         area2_mn_three,
         area2,
         area_FID,
         compound_ug_per_g_soil,
         `2F_Me`,
         `2F_FAME`,
         `2F_alk`,
         F_label_mn,
         F_label_se,
         time_course
  ) %>% 
  # Convert all unit dbls into unitless
  mutate(
    across(
      where(is.numeric),
      as.numeric
    )
  ) %>% 
  # Add assimilation efficiency data
  mutate(
    a = d2H_assim_lm_summary$a_mn,
    sa = d2H_assim_lm_summary$sa
  )
